---
title: 2014 Union Filing Report
description: Data on union election filings in 2014
hide-description: true 
execute:
        echo: false
---


```{r}

library(tidyverse)
library(gt)
library(here)
dt <- read_csv(here("gen", "data", 
  "cleaned_data.csv")
)

dt <- dt |> mutate(National=ifelse(National=="","Uncoded", National)) |> 
    mutate(National = ifelse(National_Count >1 , "Multiple", National))

all_unions <- sort(unique(dt$National))


filed <- dt |> filter( `Case_Type`=="RC")  |>
        filter(year(Date_Filed) == 2014) |> nrow()
closed <- dt |>  filter( `Case_Type`=="RC")  |>
        filter(year(Date_Closed) == 2014) |> nrow()
closed_success <- dt |>  filter( `Case_Type`=="RC")  |> 
        filter((year(Date_Closed) == 2014) &
                (Union_Cer=="Yes")) |> nrow()
median_unit <- dt |>  filter( `Case_Type`=="RC")  |> 
        filter((year(Date_Closed) == 2014) &
                (Union_Cer=="Yes")) |> pull(Num_Eligible_Voters) |>
                median()

total_unit <- dt |>  filter( `Case_Type`=="RC")  |> 
        filter((year(Date_Closed) == 2014) &
                (Union_Cer=="Yes")) |> pull(Num_Eligible_Voters) |>
                sum()

```

In 2014 there were `r scales::number(filed, big.mark=",")` representation cases filed[^note] and `r scales::number(closed, big.mark=",")` closed. Of those cases that were closed in 2014 `r scales::percent(closed_success/closed, accuracy=.1)` led to the certification of a union. The median bargaining unit for successful cases had `r scales::number(median_unit, big.mark=",")` workers. In total this led to approximately `r scales::number(total_unit, big.mark=",")` new workers with union representation. 

[^note]: This only includes cases with a single union filed, excluding the rare cases with multiple unions in an election. 

## By Union 




::: {.panel-tabset}

## Filed 
```{r}

year_dt <- dt |> filter(year(Date_Filed) == 2014)
year_dt |> arrange(desc(Date_Filed)) |> 
    mutate(National=factor(National, levels=all_unions)) |> 
    distinct() |> 
    filter( `Case_Type`=="RC")  |> 
    group_by(National) |> 
    summarize("Filed" = n(),
            "Closed"=sum(!is.na(Date_Closed)), 
            "Closed with Union"=sum(Union_Cer=="Yes"), 
            "Percent Successful"=`Closed with Union`/`Closed`, 
            "Median Successful BU"=median(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T)) |>
    complete(National, 
            fill=list("Filed"=0, 
                        "Closed"=0, 
                        "Closed with Union"=0)   ) |> 
    gt() |> 
    fmt_percent(columns=`Percent Successful`, decimals=1) |> 
    sub_missing(missing_text="-") |> 
    tab_footnote(footnote="Of those filed during the year", 
        locations=cells_column_labels(columns=3:4) ) |> 
    sub_zero(columns=`Percent Successful`, 
            zero_text="-") |>
    opt_interactive(use_pagination=FALSE)

```


## Closed
```{r}
year_dt <- dt |> filter(year(Date_Closed) == 2014)

year_dt |> arrange(desc(Date_Closed)) |> 
    mutate(National=factor(National, levels=all_unions)) |> 
    distinct() |> 
    filter( `Case_Type`=="RC")  |> 
    group_by(National) |> 
    summarize("Number Closed"=n(), 
            "Closed with Union"=sum(Union_Cer=="Yes"), 
            "Percent Unionized"=`Closed with Union`/`Number Closed`, 
            "Median Succesful BU"=median(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T), 
            "Total Workers Unionized"=sum(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T)) |>
    complete(National, 
            fill=list("Number Closed"=0, 
                        "Closed with Union"=0)   ) |> 
    gt() |> 
    fmt_percent(columns=`Percent Unionized`, decimals=1) |> 
    fmt_integer(columns=`Total Workers Unionized`) |> 
    sub_missing(missing_text="-") |> 
    sub_zero(columns=`Percent Unionized`:`Total Workers Unionized`, 
            zero_text="-") |>
    opt_interactive(use_pagination=FALSE)


```

:::


## By State


::: {.panel-tabset}

## Filed 
```{r}
full_state <- sort(c(state.abb, "DC", "PR", "VI", "SK", "GU", "AE", "AS"))

year_dt <- dt |> filter(year(Date_Filed) == 2014)
year_dt |> arrange(desc(Date_Filed)) |> 
    mutate(State=factor(State, levels=full_state)) |> 
    distinct() |> 
    filter( `Case_Type`=="RC")   |> 
    group_by(State) |> 
    summarize("Filed" = n(),
            "Closed"=sum(!is.na(Date_Closed)), 
            "Closed with Union"=sum(Union_Cer=="Yes"), 
            "Percent Successful"=`Closed with Union`/`Closed`, 
            "Median Successful BU"=median(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T)) |>
    complete(State, 
            fill=list("Filed"=0, 
                        "Closed"=0, 
                        "Closed with Union"=0)   ) |> 
    gt() |> 
    fmt_percent(columns=`Percent Successful`, decimals=1) |> 
    sub_missing(missing_text="-") |> 
    tab_footnote(footnote="Of those filed during the year", 
        locations=cells_column_labels(columns=3:4) ) |> 
    sub_zero(columns=`Percent Successful`, 
            zero_text="-") |>
    opt_interactive(use_pagination=FALSE)

```


## Closed
```{r}
year_dt <- dt |> filter(year(Date_Closed) == 2014)

year_dt |> arrange(desc(Date_Closed)) |> 
    mutate(State=factor(State, levels=full_state)) |> 
    distinct() |> 
    filter( `Case_Type`=="RC")  |> 
    group_by(State) |> 
    summarize("Number Closed"=n(), 
            "Closed with Union"=sum(Union_Cer=="Yes"), 
            "Percent Unionized"=`Closed with Union`/`Number Closed`, 
            "Median Succesful BU"=median(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T), 
            "Total Workers Unionized"=sum(Num_Eligible_Voters[Union_Cer=="Yes"], na.rm=T)) |>
    complete(State, 
            fill=list("Number Closed"=0, 
                        "Closed with Union"=0)   ) |> 
    gt() |> 
    fmt_percent(columns=`Percent Unionized`, decimals=1) |> 
    fmt_integer(columns=`Total Workers Unionized`) |> 
    sub_missing(missing_text="-") |> 
    sub_zero(columns=`Percent Unionized`:`Total Workers Unionized`, 
            zero_text="-") |>
    opt_interactive(use_pagination=FALSE)


```

:::




